---
title: "Guild Entering Events EDA"
author: "Gergely Pósfai"
date: "February 18, 2017"
output: 
    html_document:
        toc: true
        highlight: zenburn

---

<script>
window.onload = function () {
    var listElements = document.getElementsByTagName("li");
    for(i = 0;i < listElements.length; i++) {
        if (listElements[i].innerText == ""){
            listElements[i].style.display = "none";
        }
    }
}
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, fig.width = 9, fig.height = 5, cache = TRUE, cache.lazy = FALSE)
knitr::opts_knit$set(root.dir = '/mnt/cucc/bme/phd/kutatas/wow/git/wow')
```

# Introduction

This is an introductory exploratory analysis focusing on the problem of guild entering event prediction (i.e. events when avatars join guilds).

## Initialization

Setting some basic parameters, loading packages and functions, reading data:

```{r}
avatar_graph_time_window <- 30
prediction_time_window <- 7

library(dplyr)
library(lubridate)
library(data.table)
library(pROC)
library(cvTools)
library(readr)
library(igraph)
library(tidyr)
library(igraph)
library(ggplot2)
library(cowplot)
library(data.table)

source("common/init.R")
source("guild_quitting/create_intraguild_sn_timewindow.R")

prediction_dates_train <- as.character(seq(as.Date("2008-02-01"), as.Date("2008-10-25"), 7))
prediction_dates_test <- as.character(seq(as.Date("2008-11-01"), as.Date("2008-12-25"), 7))

set.seed(0)

### Add zone type column
zones <- read_csv(paste(data_dir, "zones.csv", sep = ""))
wow <- left_join(wow, zones %>%
                     select(Type, Zone_Name) %>%
                     mutate(zone_type = Type, zone = Zone_Name, Type = NULL, Zone_Name = NULL),
                 by = "zone")
rm(zones)
```

# Structured Training Dataset

We transform the original data to create a strutured dataset containing samples that can be used for guild event prediction. Each sample corresponds to a *prediction date-avatar* pair, and the target variable indicates which guild was joined by the avatar within the prediction time window after the current prediction date.

```{r}
compute_features_and_labels_pred_date <- function(data, pred_date){
    print("compute_features_and_labels --- start")
    pred_date <- as.Date(pred_date)
    testset_end_date <- pred_date + prediction_time_window

    # Keep only the data regarding known avatars
    #avatars_in_guilds <- intraguild_graphs$nodes
    #data <- data %>% filter(avatar %in% avatars_in_guilds$avatar)
    min_date <- min(data$current_date)

    ##### Compute labels for avatars
    test_data <- data %>% filter(current_date >= pred_date & current_date < testset_end_date)
    labels <- test_data %>%
        filter(event == "Guild Entered" | event == "Guild Changed") %>%
        group_by(avatar) %>%
        slice(1) %>%
        group_by() %>%
        select(avatar, current_date, guild, event, prev_guild)


    train_data <- data %>% filter(current_date < pred_date)

    # get the avatars that are not guild members on the prediction date
    # out_of_guild_avatars <- train_data %>%
    #     group_by(avatar) %>%
    #     dplyr::slice(n()) %>%
    #     group_by() %>%
    #     filter(guild == -1) %>%  # ezt kiszedni?
    #     select(avatar, guild)


    ## Features: char, race, level, number of different guild the avatar had been member of
    features <- train_data %>%
        #filter(avatar %in% out_of_guild_avatars$avatar) %>%  # ezt kiszedni?
        group_by(avatar) %>%
        summarise(
            race = race[1],
            charclass = charclass[1],
            level = max(level),
            diff_guild_count = length(unique(guild[guild != -1])))

    ### ...
    ### Compute various features here...
    ### ...

    ##### Joining labels
    print("Joining features and labels")
    features_and_labels <- left_join(features, labels, by = "avatar")
    features_and_labels$pred_date <- pred_date
    features_and_labels$testset_end_date <- testset_end_date
    features_and_labels

    features_and_labels <- features_and_labels #%>% filter(!is.na(guild))
    features_and_labels <- features_and_labels %>% mutate(known_label = ifelse(
        !is.na(guild) & guild %in% unique(train_data$guild), TRUE, FALSE))

    ##### RETURN
    print("compute_features_and_labels --- return")
    features_and_labels
}

compute_features_and_labels <- function(pred_dates){
    dataset <- data.frame()

    datasets_list <- lapply(pred_dates, function(pred_date){
        print(paste("Computing features and labels for prediction date", pred_date))
        data_subset <- compute_features_and_labels_pred_date(wow, pred_date)
        data_subset
    })
    datasets_list

    #concat result datasets
    lapply(datasets_list, function(data_subset){
        if (nrow(dataset) == 0){
            dataset <<- data_subset
        } else {
            dataset <<- rbind(dataset, data_subset)
        }
        c()
    })
    dataset
}

invisible(data_train <- compute_features_and_labels(prediction_dates_train))

# number of all samples
nrow(data_train)
# training data
glimpse(data_train)
```

# Number of Samples

Total number of samples:

```{r}
data_train %>% summarise(samples_all = n(),
                         samples_with_labels = sum(!is.na(guild)),
                         samples_with_known_labels = sum(known_label))
```

Number of samples by guilds:

```{r}
data_train %>% group_by(guild) %>%
    summarise(n = n()) %>%
    ggplot(aes(x = guild)) + geom_bar(aes(y = n), stat = 'identity') + 
    theme_bw() +
    labs(x = "Guild ID", y = "Number of Samples")
```

Number of samples by prediction date and label type:

```{r}
data_train %>%
    group_by(pred_date) %>%
    summarise(samples_all = n(),
              samples_with_labels = sum(!is.na(guild)),
              samples_with_known_labels = sum(known_label)) %>%
    gather(type, num_samples, -pred_date) %>%
    mutate(type = factor(type, levels = c("samples_all", "samples_with_labels", "samples_with_known_labels"))) %>%
    ggplot(aes(x = pred_date, y = num_samples)) +
        geom_bar(aes(fill = type),
                 stat = 'identity',
                 position = 'dodge') +
        geom_text(aes(color = type, label = num_samples),
                  position = position_dodge(width = 30),
                  angle = 45, vjust = -0.6, hjust = 0.15) +
    theme_bw() +
    labs(x = "Prediction Date", y = "Number of Samples")
```

# Percentage of Samples Belonging to Top Guilds

Percentage of samples belonging to guilds with the most samples:

```{r}
# percentage of samples corresponding to the top guildy by the number of top guilds
plot_samplepercent_of_top_guilds <- function(data){
    data <- data %>% filter(!is.na(guild))
    samples_by_guilds <- data %>% group_by(guild) %>%
        summarise(n = n()) %>% arrange(desc(n))

    samples_by_top_guilds_df <- data.frame(number_of_top_guilds = 1:nrow(samples_by_guilds)) %>%
        mutate(percent_of_samples =
                   sapply(1:max(number_of_top_guilds), function(x){sum(samples_by_guilds$n[1:x])})
               / nrow(data) * 100)

    samples_by_top_guilds_df %>%
        ggplot(aes(x = number_of_top_guilds, y = percent_of_samples)) +
        geom_line(color = "steelblue") + theme_bw() +
        labs(x = "Number of Top Guilds Owning the Most Samples", y = "Percent of Comprised Samples",
             title = paste(min(data$pred_date), max(data$pred_date), sep = "-"))
}
plot_samplepercent_of_top_guilds(data_train)
```

```{r}
selected_pred_dates <- sort(sample(unique(as.character(data_train$pred_date)), 8))
plots <- lapply(selected_pred_dates, function(current_pred_date){
    plot_samplepercent_of_top_guilds(data_train %>% filter(as.character(pred_date) == current_pred_date))
})
plot_grid(plots[[1]], plots[[2]], plots[[3]], plots[[4]], plots[[5]], plots[[6]], plots[[7]], plots[[8]], nrow = 2)
```

```{r}
# number of labeled samples of top guilds by time
top_guilds_by_time <- data_train %>%
    filter(!is.na(guild)) %>%
    group_by(guild) %>%
    mutate(samples_of_guild = n()) %>% group_by %>%
    filter(samples_of_guild > 25) %>%  # consider only the guilds that have at least N samples
    group_by(pred_date, guild) %>%
    summarise(number_of_samples = n()) %>%
    arrange(pred_date, desc(number_of_samples)) %>%
    mutate(guild = factor(guild))
head(top_guilds_by_time, 100)
```

## Autocorrelation of Number of Samples of Guilds

Check if there is any correlation between the number of samples for subsequent prediction dates for individual guilds. We only show guilds that have at least a certain number of samples.

```{r}
ggplot(top_guilds_by_time, aes(x = pred_date, y = number_of_samples, group = guild, color = guild)) +
    geom_line() +
    theme_bw() + labs(
        x = "Prediction Date",
        y = "Number of Samples",
        title = "Number of Samples with Labels by Prediction Date and Guild")
```

The same thing on a heatmap:

```{r}
ggplot(top_guilds_by_time, aes(x = pred_date, y = guild)) +
    geom_tile(aes(fill = number_of_samples), color = "white") +
    theme_bw() +
    labs(x = 'Prediction Date', 
         y = 'Guild ID', 
         title = "Number of Samples with Labels by Prediction Date and Guild") +
    #scale_fill_distiller(palette = "Spectral")
    scale_fill_gradient(low = "#ececec", high = "#000251") +
    geom_text(aes(label = number_of_samples), color = 'orange', size = 2.2)
```

The average autocorrelation of the number of samples on the subsequent prediction dates of individual guilds (the average autocorrelations for the rows of the heatmap):

```{r}
acf_values <- top_guilds_by_time %>% group_by(guild) %>% do({
    tmp <- acf(.$number_of_samples, plot = FALSE)
    result <- as.data.frame(matrix(tmp$acf, nrow = 1))
    names(result) <- paste0("lag", 0:(length(tmp$acf) - 1))
    result
})
acf_values$guild <- 0
colMeans(acf_values, na.rm = T)
```

# Creating the Network of Avatars

Few helper functions to compute the size of guilds and to construct the network of avatars on a specific prediction date:

```{r}
# get guild sizes for prediction dates
get_guild_sizes_for_pred_date <- function(pred_date){
    guild_sizes <- wow %>%
        filter(current_date < as.Date(pred_date)) %>%
        group_by(avatar) %>%
        slice(n()) %>%
        group_by(guild) %>%
        summarise(size = n()) %>%
        left_join(wow %>%
                      filter(current_date < as.Date(pred_date)) %>%
                      filter(current_date >= as.Date(pred_date) - avatar_graph_time_window) %>%
                      group_by(avatar) %>%
                      slice(n()) %>%
                      group_by(guild) %>%
                      summarise(effective_size = n())) %>%
        mutate(effective_size = ifelse(is.na(effective_size), 0, effective_size),
               pred_date = pred_date)
}
guild_sizes_by_pred_date_list <- lapply(prediction_dates_train, get_guild_sizes_for_pred_date)
guild_sizes_by_pred_date <- rbindlist(guild_sizes_by_pred_date_list)

# get the avatar network for a given prediction date
get_extended_graph_data <- function(current_pred_date){
    graph_data <- create_intraguild_graphs(wow,
                                           current_pred_date,
                                           time_window = avatar_graph_time_window)

    vertices_df <- wow %>%
        filter(current_date < as.Date(current_pred_date)) %>%
        filter(current_date >= as.Date(current_pred_date) - avatar_graph_time_window) %>%
        group_by(avatar) %>%
        slice(n()) %>% group_by() %>%
        select(avatar, guild) %>%
        left_join(data_train %>%
                      filter(pred_date == current_pred_date) %>%
                      select(avatar, label_guild = guild))

    edges_symetric <- rbind(graph_data$edges, data.frame(
        node_1 = graph_data$edges$node_2,
        node_2 = graph_data$edges$node_1,
        weight = graph_data$edges$weight
    ))
    # adding guilds to graph nodes
    edges_symetric <- edges_symetric %>%
        left_join(vertices_df %>% mutate(node_1 = avatar) %>% select(node_1, guild)) %>%
        mutate(node_1_guild = guild, guild = NULL) %>%
        left_join(vertices_df %>% mutate(node_2 = avatar) %>% select(node_2, guild)) %>%
        mutate(node_2_guild = guild, guild = NULL)

    list(graph_data = graph_data,
         vertices_df = vertices_df,
         edges_symetric = edges_symetric,
         pred_date = current_pred_date)
}
```

Construct the network of avatars for each prediction date:

```{r avatar_network_construction, results = "hide"}
avatar_network_list <- sapply(prediction_dates_train, function(current_pred_date){
    get_extended_graph_data(current_pred_date)
}, USE.NAMES = TRUE, simplify = FALSE)
edges_symetric_all <- rbindlist(lapply(avatar_network_list, function(x){
    tmp <- x$edges_symetric
    tmp$pred_date <- x$pred_date
    tmp
    }))
vertices_df_all <- rbindlist(lapply(avatar_network_list, function(x){
    tmp <- x$vertices_df
    tmp$pred_date <- x$pred_date
    tmp
}))
```

# Connectedness Between Avatars and Guilds

```{r}
get_conn_between_avatars_and_guilds <- function(current_pred_date, avatar_network){
    guild_sizes_on_pred_date <- get_guild_sizes_for_pred_date(current_pred_date)
    tmp <- avatar_network$edges_symetric %>% mutate(avatar = node_1) %>%
        filter(node_2_guild != -1) %>%
        mutate(guild = node_2_guild) %>%
        left_join(guild_sizes_on_pred_date) %>%
        mutate(guild = NULL) %>%
        left_join(avatar_network$vertices_df) %>% group_by(avatar) %>%
        summarise(degree_to_target_guild = sum(weight[node_2_guild == label_guild]),
                  degree_ratio_to_target_guild = degree_to_target_guild / size[node_2_guild == label_guild][1])

    tmp2 <- avatar_network$edges_symetric %>% mutate(avatar = node_1) %>%
        filter(node_2_guild != -1) %>%
        mutate(guild = node_2_guild) %>%
        left_join(guild_sizes_on_pred_date) %>%
        mutate(guild = NULL) %>%
        group_by(avatar, node_2_guild) %>%
        summarise(degree_to_guild = sum(weight), size = size[1]) %>%
        summarise(degree_to_guild_max = max(degree_to_guild),
                  degree_to_guild_max_guild = node_2_guild[which.max(degree_to_guild)],
                  degree_ratio_to_guild_max = max(degree_to_guild/size),
                  degree_ratio_to_guild_max_guild = node_2_guild[which.max(degree_to_guild/size)])

    node_degrees <- avatar_network$vertices_df %>%
        filter(!is.na(label_guild)) %>%
        left_join(avatar_network$edges_symetric %>% mutate(avatar = node_1) %>% group_by(avatar) %>%
                      summarise(degree_all = sum(weight))) %>%
        left_join(tmp) %>%
        left_join(tmp2) %>%
        mutate(joined_max = (label_guild == degree_to_guild_max_guild)) %>%
        left_join(guild_sizes_on_pred_date %>% 
                      mutate(label_guild = guild, label_guild_size = size) %>%
                      select(label_guild, label_guild_size, pred_date)) %>%
        mutate(joined_max_ratio = (label_guild == degree_ratio_to_guild_max_guild))

    node_degrees$pred_date <- current_pred_date
    node_degrees
}
print(class(prediction_dates_train))
node_degrees_list <- lapply(prediction_dates_train, function(current_pred_date){
    get_conn_between_avatars_and_guilds(current_pred_date, avatar_network_list[[current_pred_date]])
})
node_degrees <- rbindlist(node_degrees_list)
```

How many samples contain an avatar who joined its most connected guild:

1. If connectedness towards a guild is measured by the sum of individual connections to the members of the guild:

```{r}
summary(node_degrees$joined_max)
```

2. If connectedness towards a guild is measured as the average of the connections towards the members of the guild:

```{r}
summary(node_degrees$joined_max_ratio)
```

### Can all these be simply explained by the size of guilds? ###

#### What to look at?

Largest guilds =?= Most prevalent guilds among the target guilds where joined_max or joined_max_ratio is TRUE

```{r}
# largest guilds (most members)
guild_sizes_by_pred_date %>%
    filter(guild != -1) %>%
    select(pred_date, guild, size) %>%
    group_by(pred_date) %>%
    slice(1:min(nrow(.), 5)) %>%
    group_by() %>%
    arrange(pred_date, desc(size))
# guilds with most samples
node_degrees %>%
    group_by(pred_date, label_guild) %>%
    summarise(size = label_guild_size[1], samples = n()) %>%
    slice(1:min(nrow(.), 5)) %>%
    arrange(pred_date, desc(samples))
# guilds with the most samples where the avatar joined the most connected guild (sum of connections)
node_degrees %>%
    filter(joined_max) %>%
    group_by(pred_date, label_guild) %>%
    summarise(size = label_guild_size[1], samples = n()) %>%
    slice(1:min(nrow(.), 5)) %>%
    arrange(pred_date, desc(samples))
# guilds with the most samples where the avatar joined the most connected guild (mean connectedness)
node_degrees %>%
    filter(joined_max_ratio) %>%
    group_by(pred_date, label_guild) %>%
    summarise(size = label_guild_size[1], samples = n()) %>%
    slice(1:min(nrow(.), 5)) %>%
    arrange(pred_date, desc(samples))
```

Difference in the degree of connectedness between avatars who had joined their most connected guild and avatars who hadn't:

```{r}
summary(node_degrees$degree_to_guild_max[!is.na(node_degrees$degree_to_guild_max) & node_degrees$joined_max])
summary(node_degrees$degree_to_guild_max[!is.na(node_degrees$degree_to_guild_max) & !node_degrees$joined_max])
ggplot(node_degrees, aes(x = degree_to_guild_max)) +
    geom_density(aes(fill = joined_max, color = joined_max), alpha = 0.2) + 
    theme_bw() +
    labs(x = "Maximal Connectedness to a Guild",
         y = "Density",
         title = "Distribution of the Maximal Guild Connectednesses of Avatars",
         subtitle = "Two Groups: Whether Avatars Joined Their Most Connected Guild or Not")
```

## Distribution of Guild Connectednesses for Target and Non-Target Guilds

```{r}
get_aggregated_avatar_guild_connections <- function(current_pred_date, avatar_network){
    connectedness_to_guilds <- avatar_network$edges_symetric %>% mutate(avatar = node_1) %>%
        filter(node_2_guild != -1) %>%
        mutate(guild = node_2_guild) %>%
        left_join(guild_sizes_by_pred_date %>%
                  filter(pred_date == current_pred_date)) %>%
        mutate(guild = NULL) %>%
        group_by(avatar, node_2_guild) %>%
        summarise(degree_to_guild = sum(weight),
                  size = size[1],
                  effective_size = effective_size[1],
                  mean_degree = degree_to_guild / size,
                  effective_mean_degree = degree_to_guild / effective_size) %>%
        mutate(guild = node_2_guild, node_2_guild = NULL) %>% group_by()

    avatars_and_guilds <- expand.grid(unique(avatar_network$edges_symetric$node_1), unique(avatar_network$edges_symetric$node_2_guild), stringsAsFactors = FALSE)
    names(avatars_and_guilds) <- c("avatar", "guild")
    avatar_guild_connectedness_for_known_samples <- avatars_and_guilds %>%
        left_join(connectedness_to_guilds) %>%
        mutate(mean_degree = ifelse(is.na(mean_degree), 0, mean_degree),
               effective_mean_degree = ifelse(is.na(effective_mean_degree), 0, effective_mean_degree)) %>%
        right_join(data_train %>%
                      filter(pred_date == current_pred_date & !is.na(guild) & known_label) %>%
                      select(avatar, label_guild = guild)) %>%
        mutate(is_target_guild = (!is.na(label_guild) & label_guild == guild))

    connectedness_to_guilds$pred_date <- current_pred_date
    avatar_guild_connectedness_for_known_samples$pred_date <- current_pred_date

    list(all_avatar_guild_conns = connectedness_to_guilds,
        known_samples = avatar_guild_connectedness_for_known_samples)

}

avatar_guild_connectedness_list <- lapply(prediction_dates_train, function(current_pred_date){
    get_aggregated_avatar_guild_connections(current_pred_date, avatar_network_list[[current_pred_date]])
})
avatar_guild_connectedness_all_conns <- rbindlist(
    lapply(avatar_guild_connectedness_list, function(x){x$all_avatar_guild_conns}))
avatar_guild_connectedness_known_samples <- rbindlist(
    lapply(avatar_guild_connectedness_list, function(x){x$known_samples}))
```

If connectedness is measured by the effective mean degree (the mean connectedness to active guild members):

```{r}
avatar_guild_connectedness_known_samples %>% filter(effective_mean_degree > 5) %>%
    ggplot(aes(x = effective_mean_degree)) +
    geom_density(aes(fill = is_target_guild, color = is_target_guild), alpha = 0.2) + theme_bw()
```

If connectedness is measured by the simple mean degree (the mean connectedness to guild members):

```{r}
avatar_guild_connectedness_known_samples %>% filter(mean_degree > 5) %>%
    ggplot(aes(x = mean_degree)) +
    geom_density(aes(fill = is_target_guild, color = is_target_guild), alpha = 0.2) + theme_bw()
```

## Histogram of the connectedness ranks of target guilds

*Connectedness rank*: for each avatar guilds are sorted in descending order according to their connectedness to the given avatar. The rank is the position of the avatar's target guild in this list.

```{r}
target_guild_connectedness_with_ranks <-
    avatar_guild_connectedness_all_conns %>%
    group_by(pred_date, avatar) %>%
    arrange(desc(effective_mean_degree)) %>%
    #arrange(desc(mean_degree)) %>%
    mutate(rank = seq_along(effective_mean_degree)) %>%
    group_by() %>%
    right_join(data_train %>%
                  mutate(pred_date = as.character(pred_date)) %>%
                  filter(#pred_date == "2008-02-01" &
                             !is.na(guild) & known_label) %>%
                  select(avatar, pred_date, label_guild = guild)) %>%
    filter(!is.na(label_guild) & label_guild == guild)
# histogram:
ggplot(target_guild_connectedness_with_ranks, aes(x = rank)) +
    geom_histogram(binwidth = 1, fill = 'steelblue', alpha = 0.6) + theme_bw() +
    labs(title = "Rank of a Sample:", subtitle = "Which most connected guild is the target guild")
# density function:
#ggplot(target_guild_connectedness_with_ranks, aes(x = rank)) +
#    geom_density(fill = 'steelblue', alpha = 0.6) + theme_bw() +
#    labs(title = "Rank of a Sample:", subtitle = "Which most connected guild is the target guild")
```

# Connectedness Between Target Avatars and Other Avatars

```{r}
tmp3 <- edges_symetric_all %>% mutate(avatar = node_1) %>%
    filter(node_2_guild != -1) %>%
    group_by(avatar, pred_date) %>% # ide a group_by-hoz hozzáadni a pred_date-t
    arrange(desc(weight)) %>%
    slice(1:10) %>%
    mutate(rank1 = paste0("rank-", seq_len(n()), "-guild")) %>%
    mutate(rank2 = paste0("rank-", seq_len(n()), "-weight")) %>%
    select(avatar, weight, node_2_guild, node_2, rank1, rank2) %>% # ide is pred_date
    group_by()

tmp4 <- tmp3 %>%
    group_by(pred_date) %>% #talán így jó lesz
    select(avatar, node_2_guild, rank1) %>%
    spread(key = rank1, value = node_2_guild) %>%
    group_by()

tmp5 <- tmp3 %>%
    group_by(pred_date) %>% #talán így jó lesz
    select(avatar, weight, rank2) %>%
    spread(key = rank2, value = weight) %>%
    group_by()

node_degrees_to_nodes <- vertices_df_all %>%
    filter(!is.na(label_guild)) %>%
    left_join(edges_symetric_all %>% mutate(avatar = node_1) %>% group_by(avatar) %>%
                  summarise(degree_all = sum(weight))) %>%
    left_join(tmp4) %>%
    left_join(tmp5)

nrow(node_degrees_to_nodes)
head(node_degrees_to_nodes)
```


Distribution of edge weights towards other avatars by their guild (target/non-target). Note that only the avatars of the training data are considered (i.e. avatars with no guilds on the current prediction date):

```{r}
node_degrees_to_nodes_all <-
    edges_symetric_all %>% mutate(avatar = node_1) %>%
    filter(node_2_guild != -1) %>%  # ez ki is veheto
    right_join(data_train %>%
                   mutate(pred_date = as.character(pred_date)) %>%
                   mutate(label_guild = guild) %>%
                   #filter(known_label) %>%
                   filter(!is.na(label_guild)) %>%
                   select(avatar, label_guild, pred_date)
    ) %>%
    mutate(to_target_guild = !is.na(label_guild) & !is.na(node_2_guild) & label_guild == node_2_guild)
node_degrees_to_nodes_all %>% filter(weight > 5) %>%
    ggplot(aes(x = weight)) + #xlim(0, 200) +
    geom_density(aes(fill = to_target_guild, color = to_target_guild), alpha = 0.2) + theme_bw()
```

Ratio of target guild edges and other edges by the number of included top connections of avatars:

```{r}
all_edges <- node_degrees_to_nodes_all %>% group_by(to_target_guild) %>% summarise(n = n())

top_edges <- edges_symetric_all %>% mutate(avatar = node_1) %>%
    filter(node_2_guild != -1) %>%
    group_by(avatar, pred_date) %>%
    arrange(desc(weight)) %>%
    slice(1:10) %>%
    mutate(rank = paste0("top-", seq_len(n()))) %>%
    select(avatar, weight, node_2_guild, node_2, rank, pred_date) %>%
    group_by()

num_edges_by_number_of_top_connections <-
    top_edges %>%
    right_join(data_train %>%
                   mutate(pred_date = as.character(pred_date)) %>%
                   mutate(label_guild = guild) %>%
                   #filter(known_label) %>%
                   filter(!is.na(label_guild)) %>%
                   select(avatar, label_guild, pred_date)) %>%
    filter(!is.na(weight)) %>% group_by(rank) %>%
    summarise(edges_to_target_guild = sum(node_2_guild == label_guild),
              edges_to_other_guilds = n() - edges_to_target_guild)

num_edges_by_number_of_top_connections2 <- as.data.frame(t(
    sapply(seq_len(nrow(num_edges_by_number_of_top_connections)), function(x){
        rank_values <- paste0("top-", 1:x)
        tmp <- num_edges_by_number_of_top_connections %>%
            filter(rank %in% rank_values)
        edges_to_other_guilds <- sum(tmp$edges_to_other_guilds)
        edges_to_target_guild <- sum(tmp$edges_to_target_guild)
        c(rank = paste0("top-", x),
          to_target_guild = edges_to_target_guild / (edges_to_target_guild + edges_to_other_guilds),
          to_other_guilds = edges_to_other_guilds / (edges_to_target_guild + edges_to_other_guilds))
}))) %>%
    mutate(rank = as.character(rank),
           to_target_guild = as.double(as.character(to_target_guild)),
           to_other_guilds = as.double(as.character(to_other_guilds))) %>%
    rbind(data.frame(rank = "All Edges",
                          to_target_guild = all_edges$n[all_edges$to_target_guild] / sum(all_edges$n),
                          to_other_guilds = all_edges$n[!all_edges$to_target_guild] / sum(all_edges$n)))

num_edges_by_number_of_top_connections2 %>%
    gather(key = type, value = edges_percent, -rank) %>%
    mutate(rank = factor(rank, levels =
                             c(paste0("top-",1:nrow(num_edges_by_number_of_top_connections)), "All Edges"))) %>%
    ggplot(aes(x = rank, y = edges_percent)) +
    geom_bar(aes(fill = type), stat = 'identity', position = 'dodge') +
    #geom_text(aes(label = paste0(100 * round(edges_percent, 4), "%"), color = type),
    #          position = position_dodge(width = .8), angle = 45, vjust = -0.6, hjust = 0.15) +
    geom_label(aes(label = paste0(100 * round(edges_percent, 4), "%"), fill = type),
              position = position_dodge(width = .8), vjust = -0.2, alpha = 0.65, color = 'white') +
    theme_bw() +
    labs(x = "How Many of the Avatars' Top-Weight Edges Are Considered",
         y = "Percentage of Various Types of Edges",
         title = "Percentage of Edges that Go to the Members Of the Target Guild",
         subtitle = "Within Different Subsets of the Avatars' Top-Weight Edges")
```
